Reading Notes

### 2020-07-08 paper.tex
finished lee 2011

\cite{Vehoff2010a}
rubrene record charge carrier $15 \frac{cm^{2}}{V s}$ single crystal by vapor deposition. typical for thin-film is $1 \frac{cm^{2}}{V s}$

Today I'm digging around in more of the votca stuff to try and figure out how to run kmc there. They use ORCA too! Also their tutorials and documentation REALLY SUCK. [https://github.com/votca/xtp-tutorials](https://github.com/votca/xtp-tutorials) in particular I'm looking at LAMMPS/KMC\_Thiophene.
OK. either I am dumb or that tutorial sucks. I can tell that they're using orca and the inputs/oputputs the use but there's no explanation of what they're doing. It looks like they calculate the reorganization energy, but they don't define a chromophore--which makes sense for thiophene but what about when your molecule is ginormous?
\cite{Ruhle2011b} discusses charge transport in amorphous films of [tris-(8-hydroxyquinoline)aluminum](https://en.wikipedia.org/wiki/Tris(8-hydroxyquinolinato)aluminium). Oh Figure 1 is nice--it is a workflow of what can be done in votca.
11A talks about how to parameterize new contributions to a force-field using first-principles.
11B choosing a "chromophore"-- rigid fragments vs conjugated segments. they broke apart the chromophore in a polymer like p3ht using the dihedral angle--although they validated this choice with other methods. Interesting-- they replace the chromophores with those which have been geometry optimized using DFT. then they make a neighbor list
I'll come back to this paper later. I at least was able to answer some of my questions about choosing a chromophore.
11C talks about calculating the transfer integral for each pair and why ZINDO works and when it breaks down.

@@

Reading \cite{Hanson2016} also my mendeley overwriting my files because it thinks they are duplicates or something? It keeps losing the pdf even though I've uploaded it. :(
SMILES - simplified molecular-input line-entry system
SMARTS - smiles arbitrary target specification
around since 1980s
alternatives SLN, MQL, CSRML.
This paper is about specifically Jmol smiles so I'm skipping to a different one.
\cite{Weininger1988} First paper about smiles- how do we unambiguously represent a chemical structure? historically CAS, graph theory, IUPAC.
human-readable and machine readable
hydrogens, single bond don't need to be specified. designed for organic molecules.

\cite{Smith2018} reading about psi4: free and open source with python api that uses blas and c under the hood. has jupyter notebooks tutorials. This paper reads like our perspective paper in tone :hearteyes: 2.2 -2.3 kinda lost me. I should look at their jupyter notebooks.

Today searched "coarse grain backmapping" in the library and got the following papers:
\cite{Alessandri2017b}

@@

\cite{Haxton2015a}
CG beads with orientation. They use the word "stiffest" to describe degrees of freedom--they mean bond stretching, angle bending, and torsion within rings. They suggest there are two separate ways to improve CG: better mapping between AA and CG or better CG interactions. The seconds can be helped with IBI, entropy minimization... First one is what the authors will focus on.
Point-site method maps groups of atoms onto a bead--bead potential is spherically symmetric, but some models use neighboring sites to introduce some directionality. e.g., Alemani et al created a protein model where the dipole interaction was a function of the alpha-carbon angle. Here they add orientation to the point-site model. This increases the degrees of freedom for each site from 3 to 6, but they model bonds and angles as stiff and dihedral angles (except rings and double bonds) as soft. They also map about 8 atomns to a site. They use backmapping from ref 64--not backwards.py. 
They simplify the ideal interactions of the CG model (many-body problem) to pai potentials. They show how to calculate to error in an observable calculated on backmapped structure. C code used for backmapping in SI.
mapping ratio - atomic DOF / CG DOF. PRIMO on average is 3.0, UNRES, MARTINI, MS-CG are 8.2, 7.1, and 6.0. I think this paper aims to improve on PRIMO by adding directionality? they measure accuracy with rmsd and efficiency with mapping ratio.

@@

\cite{Poblete2018a}
RNA - backmapping steered MDaimed at minimizing a particular RMSD (ERMSD) between atomic and target structure. target structure were found to be recovered by this backmapping except in the case where there were unpaired bases. folding pathway dependent on parameters used in ERMSD.
need AA strutures to validate with experiment (x-ray or neutron scattering) backmapping usually involves placing atomistic coordinates relative to the beads and then minimizing the energy of the structure using steepest descent or short MD runs (could use position restraint). Atomistic can even be mapped onto the whole trajectory. 
This work describes the backmapping of the SPlit and conQueR (SPQR) method. Minimizes the ERMSD distance between solvated AA strand of the CG structure (RNA). ERMSD : origin is set to CoM of C2 C4 and C6 atoms of each base (see ref 23), then for each pair of bases, rij is the center of base i in the coord system of base j. In order to account for anisotropy, the scaling for the z-direction is different (does this mean the strand is oriented to z in some way??) This metric shows the difference between arrangement of nucleobases of two RNA structures. Backbone and sugar interactions are unrestrained. The paper will show results on the backbone conformation. They use steered MD with ERMSD as the steering parameter. (How does steered MD work?) Look like they use and external pulling force which depend on ERMSD.

@@

\cite{Mikhnenko2012}
Exciton diffusion length (EDL) in narrow bangap polymers. photoluminescense decay time is related and measurable. PCBM and PCDTBTs modeled with Monte Carlo--code available. They used P3HT as reference (5.4+/-0.7nm exciton diffusion length). 
Exciton diffusion is essential for organic solar cells. excitons are electron hole pairs created by excitation due to light absorption. they are separated into free charges at an interface which creates current. the movement of the excitons through hopping is what is refered to as diffusion. Exciton diffusion length is a factor in device efficiency.
Other methods to measure EDL are fluorescence quenching - the dependence of the exciton quenching efficiency vs semiconductor thickness is fit to 1D diffusion equation. Pros: direct measuremnt, cons: difficult experimentally and there are many things to consider in the model (FRET, effect of polymer-vaccuum interface, optical interference). 
This paper uses MC to model PL decay.
(Losing focus come back tomorrow)

@@

Review of state-of-the-art OPV BHJ solar cells. 
pros: thin/light, semitransparent, cheap, continuous production process, short payback times, easy to integrate into new and existing products. 
History of development from 2001 2.5\% PCE to 2011 10\% PCE. Most degrade when exposed to air and sunlight within a few years. Molecular structure including side chains affects stability. Electron affinity of the acceptor determines degradation rate of the semiconductor. Changing the elctrode and using the inverted design(? read waldauf) helps the electrode oxidation. This requires no vacuum
They discuss BHJ morphology and how the A and D regions need to be small enough that an exciton could find it's way to an interface but not so small that once the charge is separated and current is generated at that interface that the current couldn't get to the electrode. The ideal is an interlocked comb structure but in reality solution processed OPVs form patches. This review is not about morphology (they recommened Hoppe2004). Morphology can only effect the efficiency of an AD pair, not the ultimately efficiency limit. This depends on the bandgap and electron affinities of the DA moeities.
fig 5 explains inverted design a bit. 
They discuss costs and efficiencies. Should probably read about Shockley Queisser Limit. (ref 47) based on analysis of pn solar cell they say the max efficiency is 30\% and the optimum band gap in 1.1 eV. Archer and Bolton roughly confirm this -- much of the light energy is lost because the photon is too small to excite the absorber, other loss is due to intraband thermalization of charge carriers (?), 12\% entropic loss, 1\% radiative recombination. Assumption of the Shockley Queisser limit
1. each absorbed photon generates and e/hole pair
2. perfect charge collection
3. radiative recombination as the only recombination.
Based on this work and the external radiative efficiency (ERE) proposed by Green, and actual max of 15-16\% efficiency is predicted.
(continue from 5)

@@

Overview of organic solar cells. sp2 hybridization of carbon is what allows organics to absorb in the uv-vis range. (conjugated pi orbitals.) In comparison, inorganic semiconductors have low mobilities but very high absorption coefficients. The exciton diffusion length is shorter in OPVs too.
Most OPV are hole conductors and have band gap around 2 eV, which is higher than silicon. But the ability to modify and tune the chemistry as well as the cheap, mass production makes OPVs enticing.
history: 
first OPVs were single organics layers sandwiched between two metals with different work functions. (Evac - Efermi) 0.7\% PCE
next bilayer heterojuctions-- two organic layers between electrodes (e.g. perylene and phtalocyanine) 1\% PCE
C60 introduced, polymer fullerene bilayer heterojunction.
Bulk heterojunction 2\% PCE
(This article only discusses up to 4\% PCE and does not provide specific explanation for the increase)
common structure is hole-conducting polymer with electron acceptor (C60 as in PCBM). Solution processable due to side chains. Preferential orientation of polymer backbones parallel to the substrate gives rise to anisotropic CT. In BHJ cells CT is sensitive to the morphology.
OPV energy generation steps: 
1. absorption
2. exciton diffusion
3. charge separation
4. charge transport
PCE depends on # photons absorbed, dissociated, and that reach the electrode. Number absorbed depends on the absorption spectrum, absorption coefficient and layer thickness. The fraction of excitons which dissociate depends on the exciton dissociation length and the charge separation probability at the interface. Finally the the number of charges which reach the electrode depends on the driving force or gradient resulting from the potentials of the elctrons and holes. thin films (<100nm) are usually field drift dominated others have enough screening are dominated by concentration gradients at the contacts.
I skipped over devices.
concepts for improvement:
metal electrodes quench electrons in C60 so an transparent, exciton-blocking layer is between electrode and layer with C60. ultrathin LiF interfacial layer is one example. 
Increase the absorption range. smaller band gap <2eV ~800-900 nm.
morphology controls. to control size of fullerene domains in p3ht/fullerene, a plasticizer was added. This increase miscibility of polymer and fullerene creating smaller domains. Solvent/evaporation time, surface interaction, and annealing all have a large effect of the morphology.

@@

\cite{Halls1995}
another older paper. Cavendish lab! Photovoltaic effect - production of electrons/holes under illumination. Molecular semiconductors produce excitons instead of free charges. Charge collection requires dissociation, which is efficient at interfaces of different electron affinities and ionization potentials. (electron goes to larger electron affinity and hole to lower ionization potential.) A layered structure then seems ideal, but Exciton diffusion length is much shorter than the absorption depth. so an interpenetrating network is shwon in this paper to be ideal.
poly-phenylenevinylene derivitive mixture MEH-PPV and CN-PPV. spin coating on glass slide. they claim phase separation on the scale of 10-100nm this measurement relied on ferric chloride doping MEH-PPV but not the CN derivitive.
The current vs Voltage graph for the mixture was very different under illumination.
they predict these sort of flexible polymer photodetectors will be useful in medical imaging.

\cite{Gartner2019a}
Somehow didn't add this!
University of delaware. There is a Jankowski/Marsh image in Fig 1!
OMG I just realised this is Arthi from the MoSDeF calls. :D No wonder this paper is so approachable!! 
Atomistic structures, not always more accurate, can't compute polymer chain level rearrangement
CG -- chemists might not like them but physicists do
atomistic simulations are good when you already know the chain configuration at a state point. Atomistic FF are still tailored to fit the properties of specific systems. got distracted today... will continue with II.B tomorrow
OK back to it
CG - intermediate resolution (group of atoms within a monomer), CG monomer (whole monomer), mesoscale CG model (group of monomers on the length of a Kuhn segment or the whole chain.
Finer models are parameterized to represent specific chemistries while coarse models are more generic. finer models can be parameterized with IBI for structure or force matching or relative entropy matching. the level of coarseness should depend on what features you want to examine.
MARTINI - generic model 3-5 heavy atoms are grouped together each bead is assigned polar/apolar/donor/acceptor etc based on the chemistry/connectivity.
soft potentials can be used for CG beads like DPD -- can have unphysically high compressibility
!!! Systematic coarse graining approaches refs (87,91,269-273)
start reading tomorrow at pt III

@@

\cite{Reith2003a}
IBI algorithm is made in this paper! Uses potentials of mean force. IBI potentials are nontransferrable--they work best for the system they are optimized for.
CG allows chain behavior to be studied. History: bead spring polymer chains in a melt to a soft-core liquid ellipsoidal particles with anisotropic gaussian potential. polymer melt cg-ing. None of these derived an automated optimization scheme to conserve the chemical nature of the underlying atomistic model in a standardized way as we do.
PRISM theory combined with MC can predict long and short range structures of polymer chains but can't produce CG potentials.
Reverce MC can reproduce RDF without a need for potential. lack of potential limits usefulness though because RMC uses knowledge of RDF without knowing underlying forces.
Description of IBI algorithm: potential of mean force IS boltzmann inversion of RDF. (Free energy NOT potential energy.) Bending potentials before nonbonded potentials.
They used a five point running average to smooth the potentials
bond stretch -> angle bend -> nonbonded -> dihedral
They started with monoatomic liquids with LJ and WCA potentials (1) they used the correct potential as V0. (2) then they used the boltzmann inverse of the RDF. 
Conclusions:
start with small range (cutoff?) and increase until RDF matches. CG FF for polyisoprene are different between solution and melt.

\cite{Ayton2007a}
Coarse graining scheme, systematic, for biological systems.
If CGing is done systematicall it retains important averaged atomistic level interations. Connecting length and time scales.Systematic methods for making CG systems: RMC, this paper will focus on multiscale coarse graining (MS-CG) uses force matching algorithm
Variational. Some of the math does not make sense but it appears to only be based on positions of atomistic and CG particles. They make the free energies of the atomisitic and CG systems the same. Many atomistic frames are mapped to CG beads and the potentials are based in the gradient of the forces felt by the beads. The algorithm minimizes a residual function.
Summary: works, RDFs match. Enables calculation of CG force fields without resolving many-dimensional potential of mean force. (but honestly IBI seems so much simpler. Is there something I'm missing? is boltzmann inverse of RDF not PMF?? This paper was published after Reith paper... when is force matching better?)

\cite{Peter2009c}
Review paper- coarse grained models linked to atomistic models. 
They mention the good, marginal, and poor solvent parameter Theta.
models can be linked sequentially, hybrid - both level present at once and interacting, or adaptive - individual molecules switch on the fly depending on e.g., spatial coordinates.
CG target can be thermodynamic or structural.
Structure based: boltzmann inversion of distribution with constant to set minimum to 0. Free energy vs PMF? Boltzmann inversion usually results in a tabulated potential but by fitting to gaussians it can be mapped to an analytical function.
Bonded potential can be determined on a single polymer chain in vacuo but then the nonbonded interactions have to be considered carefully to avoid double counting. However bonded and nonbonded can be obtained from the same atomistic simulation of polymer melt iteratively. This makes the potentials interdepent.
IBI can also consider other thermodynamic quantities like pressure and compressibility. IBI not useful for dilute solutions
start next time at backmapping
backmapping has no one unique soln. every CG structure corresponds to an ensemble of atomistic microstates. reinsert theatomistic structure so that the atoms still satisfy the CG mapping and then relax the atoms with position restraint to the CG position.
CG backmapped to atomistic allows better comparison with experiment than atomistic alone by giving access to larger length and time scales. e.g., NMR timescales are too long to simulate with atomistic alone, yet atomistic coordinates are necessary.
Dynamics: the CG model is independent and has it's own timestep. dynamics are accelerated.

@@

\cite{Brini2013}
review of systematic coarse-graining for soft materials
focuses on representability (how well a system predicts properties at the statepoint it was optimized for) and transferrability ( how well it can be used for other statepoints.)
effective pair potentials are used for CG instead of the expensive many-body potentials. averaging over fast degrees of freddom removes their entropic contribution. to compensate for this, the pair potentials are softer resulting in a smoothed energy landscape. this affects the thermodynamic properties-- e.g., the heat capacity, which is related to the entropy fluctions at constant t and p is underestimated by a cg model (because the fluctuations arent as large). while compressibility related to volume fluctuation will be over estimated (i think because the potentials are so soft.) The thermal expansion coefficient which is related to both may well be represented accurately.
parameterized vs derived CG potentials - 1st one atomistic simulations are used to calculate target properties (pair correlations, force distributions) IBI is this. 2nd one atomistic interaction are used directly. not optimized to reproduce selected tragets, therefore all properties are predictions of the model.
Parameterized methods: IBI method described. 
Inverse Monte Carlo - also an iteractive scheme that corrects a guessed interaction potential in order to reproduce a target radial distribution function, but the guess is based on statistical mechanics that take into account that a variation of the potential at a given distance r can lead to a variation of the RDF at all other distances. more expensive than IBI requires longer sims to calculate correlations. Can also include target thermo properties like surface tension.
Both IBI and IMC are cases of relative entropy -- a measure of the amount of information lost upon coarse-graining and is defined in term of propability distributions of atomistic and CG systems. both methods minimize the discrepancy between the atomistic and CG distributions.
Another method is force matching. effective pair potentials match the mean force on a particle through the atomistic force field.
Derived methods: These potentials have a clear physical meaning (why?) potential of mean force calculated at LOW concentration. fragment based coarse graining
skipped ahead to polymers
polymers are important for cg because the volumes needed to observe their long length scale properties in atomistic md are prohibitively expensive. pressure-corrected IBI scheme for polystyrene matched gyration radius and Flory characteristic ratio at 500 K. (flory ratio relates to chain stiffness?) but entanglement length was overestimated.

\cite{Murtola2009a}
quick letter - to get the full picture we have to consider multiple length scales. abstracting small length scales is necessary for time/resources. probably dont include this in references, it's so short.

>>>>

\cite{Vehoff2010a}

rubrene record charge carrier $15 \frac{cm^{2}}{V s}$ single crystal by vapor deposition. typical for thin-film is $1 \frac{cm^{2}}{V s}$

Today I'm digging around in more of the votca stuff to try and figure out how to run kmc there. They use ORCA too! Also their tutorials and documentation REALLY SUCK. [https://github.com/votca/xtp-tutorials](https://github.com/votca/xtp-tutorials) in particular I'm looking at LAMMPS/KMC\_Thiophene.
OK. either I am dumb or that tutorial sucks. I can tell that they're using orca and the inputs/oputputs the use but there's no explanation of what they're doing. It looks like they calculate the reorganization energy, but they don't define a chromophore--which makes sense for thiophene but what about when your molecule is ginormous?

\cite{Ruhle2011b}

discusses charge transport in amorphous films of [tris-(8-hydroxyquinoline)aluminum](https://en.wikipedia.org/wiki/Tris(8-hydroxyquinolinato)aluminium). Oh Figure 1 is nice--it is a workflow of what can be done in votca.
11A talks about how to parameterize new contributions to a force-field using first-principles.
11B choosing a "chromophore"-- rigid fragments vs conjugated segments. they broke apart the chromophore in a polymer like p3ht using the dihedral angle--although they validated this choice with other methods. Interesting-- they replace the chromophores with those which have been geometry optimized using DFT. then they make a neighbor list
I'll come back to this paper later. I at least was able to answer some of my questions about choosing a chromophore.
11C talks about calculating the transfer integral for each pair and why ZINDO works and when it breaks down.

@@

Reading

\cite{Hanson2016}

also my mendeley overwriting my files because it thinks they are duplicates or something? It keeps losing the pdf even though I've uploaded it. :(
SMILES - simplified molecular-input line-entry system
SMARTS - smiles arbitrary target specification
around since 1980s
alternatives SLN, MQL, CSRML.
This paper is about specifically Jmol smiles so I'm skipping to a different one.

\cite{Weininger1988}

First paper about smiles- how do we unambiguously represent a chemical structure? historically CAS, graph theory, IUPAC.
human-readable and machine readable
hydrogens, single bond don't need to be specified. designed for organic molecules.

\cite{Smith2018}

reading about psi4: free and open source with python api that uses blas and c under the hood. has jupyter notebooks tutorials. This paper reads like our perspective paper in tone :hearteyes: 2.2 -2.3 kinda lost me. I should look at their jupyter notebooks.

Today searched "coarse grain backmapping" in the library and got the following papers:

\cite{Alessandri2017b}

@@

\cite{Haxton2015a}

CG beads with orientation. They use the word "stiffest" to describe degrees of freedom--they mean bond stretching, angle bending, and torsion within rings. They suggest there are two separate ways to improve CG: better mapping between AA and CG or better CG interactions. The seconds can be helped with IBI, entropy minimization... First one is what the authors will focus on.
Point-site method maps groups of atoms onto a bead--bead potential is spherically symmetric, but some models use neighboring sites to introduce some directionality. e.g., Alemani et al created a protein model where the dipole interaction was a function of the alpha-carbon angle. Here they add orientation to the point-site model. This increases the degrees of freedom for each site from 3 to 6, but they model bonds and angles as stiff and dihedral angles (except rings and double bonds) as soft. They also map about 8 atomns to a site. They use backmapping from ref 64--not backwards.py. 
They simplify the ideal interactions of the CG model (many-body problem) to pai potentials. They show how to calculate to error in an observable calculated on backmapped structure. C code used for backmapping in SI.
mapping ratio - atomic DOF / CG DOF. PRIMO on average is 3.0, UNRES, MARTINI, MS-CG are 8.2, 7.1, and 6.0. I think this paper aims to improve on PRIMO by adding directionality? they measure accuracy with rmsd and efficiency with mapping ratio.

@@

\cite{Poblete2018a}

RNA - backmapping steered MDaimed at minimizing a particular RMSD (ERMSD) between atomic and target structure. target structure were found to be recovered by this backmapping except in the case where there were unpaired bases. folding pathway dependent on parameters used in ERMSD.
need AA strutures to validate with experiment (x-ray or neutron scattering) backmapping usually involves placing atomistic coordinates relative to the beads and then minimizing the energy of the structure using steepest descent or short MD runs (could use position restraint). Atomistic can even be mapped onto the whole trajectory. 
This work describes the backmapping of the SPlit and conQueR (SPQR) method. Minimizes the ERMSD distance between solvated AA strand of the CG structure (RNA). ERMSD : origin is set to CoM of C2 C4 and C6 atoms of each base (see ref 23), then for each pair of bases, rij is the center of base i in the coord system of base j. In order to account for anisotropy, the scaling for the z-direction is different (does this mean the strand is oriented to z in some way??) This metric shows the difference between arrangement of nucleobases of two RNA structures. Backbone and sugar interactions are unrestrained. The paper will show results on the backbone conformation. They use steered MD with ERMSD as the steering parameter. (How does steered MD work?) Look like they use and external pulling force which depend on ERMSD.

@@

\cite{Mikhnenko2012}

Exciton diffusion length (EDL) in narrow bangap polymers. photoluminescense decay time is related and measurable. PCBM and PCDTBTs modeled with Monte Carlo--code available. They used P3HT as reference (5.4+/-0.7nm exciton diffusion length). 
Exciton diffusion is essential for organic solar cells. excitons are electron hole pairs created by excitation due to light absorption. they are separated into free charges at an interface which creates current. the movement of the excitons through hopping is what is refered to as diffusion. Exciton diffusion length is a factor in device efficiency.
Other methods to measure EDL are fluorescence quenching - the dependence of the exciton quenching efficiency vs semiconductor thickness is fit to 1D diffusion equation. Pros: direct measuremnt, cons: difficult experimentally and there are many things to consider in the model (FRET, effect of polymer-vaccuum interface, optical interference). 
This paper uses MC to model PL decay.
(Losing focus come back tomorrow)

@@

Review of state-of-the-art OPV BHJ solar cells. 
pros: thin/light, semitransparent, cheap, continuous production process, short payback times, easy to integrate into new and existing products. 
History of development from 2001 2.5\% PCE to 2011 10\% PCE. Most degrade when exposed to air and sunlight within a few years. Molecular structure including side chains affects stability. Electron affinity of the acceptor determines degradation rate of the semiconductor. Changing the elctrode and using the inverted design(? read waldauf) helps the electrode oxidation. This requires no vacuum
They discuss BHJ morphology and how the A and D regions need to be small enough that an exciton could find it's way to an interface but not so small that once the charge is separated and current is generated at that interface that the current couldn't get to the electrode. The ideal is an interlocked comb structure but in reality solution processed OPVs form patches. This review is not about morphology (they recommened Hoppe2004). Morphology can only effect the efficiency of an AD pair, not the ultimately efficiency limit. This depends on the bandgap and electron affinities of the DA moeities.
fig 5 explains inverted design a bit. 
They discuss costs and efficiencies. Should probably read about Shockley Queisser Limit. (ref 47) based on analysis of pn solar cell they say the max efficiency is 30\% and the optimum band gap in 1.1 eV. Archer and Bolton roughly confirm this -- much of the light energy is lost because the photon is too small to excite the absorber, other loss is due to intraband thermalization of charge carriers (?), 12\% entropic loss, 1\% radiative recombination. Assumption of the Shockley Queisser limit
1. each absorbed photon generates and e/hole pair
2. perfect charge collection
3. radiative recombination as the only recombination.
Based on this work and the external radiative efficiency (ERE) proposed by Green, and actual max of 15-16\% efficiency is predicted.
(continue from 5)

@@

Overview of organic solar cells. sp2 hybridization of carbon is what allows organics to absorb in the uv-vis range. (conjugated pi orbitals.) In comparison, inorganic semiconductors have low mobilities but very high absorption coefficients. The exciton diffusion length is shorter in OPVs too.
Most OPV are hole conductors and have band gap around 2 eV, which is higher than silicon. But the ability to modify and tune the chemistry as well as the cheap, mass production makes OPVs enticing.
history: 
first OPVs were single organics layers sandwiched between two metals with different work functions. (Evac - Efermi) 0.7\% PCE
next bilayer heterojuctions-- two organic layers between electrodes (e.g. perylene and phtalocyanine) 1\% PCE
C60 introduced, polymer fullerene bilayer heterojunction.
Bulk heterojunction 2\% PCE
(This article only discusses up to 4\% PCE and does not provide specific explanation for the increase)
common structure is hole-conducting polymer with electron acceptor (C60 as in PCBM). Solution processable due to side chains. Preferential orientation of polymer backbones parallel to the substrate gives rise to anisotropic CT. In BHJ cells CT is sensitive to the morphology.
OPV energy generation steps: 
1. absorption
2. exciton diffusion
3. charge separation
4. charge transport
PCE depends on # photons absorbed, dissociated, and that reach the electrode. Number absorbed depends on the absorption spectrum, absorption coefficient and layer thickness. The fraction of excitons which dissociate depends on the exciton dissociation length and the charge separation probability at the interface. Finally the the number of charges which reach the electrode depends on the driving force or gradient resulting from the potentials of the elctrons and holes. thin films (<100nm) are usually field drift dominated others have enough screening are dominated by concentration gradients at the contacts.
I skipped over devices.
concepts for improvement:
metal electrodes quench electrons in C60 so an transparent, exciton-blocking layer is between electrode and layer with C60. ultrathin LiF interfacial layer is one example. 
Increase the absorption range. smaller band gap <2eV ~800-900 nm.
morphology controls. to control size of fullerene domains in p3ht/fullerene, a plasticizer was added. This increase miscibility of polymer and fullerene creating smaller domains. Solvent/evaporation time, surface interaction, and annealing all have a large effect of the morphology.

@@

\cite{Halls1995}

another older paper. Cavendish lab! Photovoltaic effect - production of electrons/holes under illumination. Molecular semiconductors produce excitons instead of free charges. Charge collection requires dissociation, which is efficient at interfaces of different electron affinities and ionization potentials. (electron goes to larger electron affinity and hole to lower ionization potential.) A layered structure then seems ideal, but Exciton diffusion length is much shorter than the absorption depth. so an interpenetrating network is shwon in this paper to be ideal.
poly-phenylenevinylene derivitive mixture MEH-PPV and CN-PPV. spin coating on glass slide. they claim phase separation on the scale of 10-100nm this measurement relied on ferric chloride doping MEH-PPV but not the CN derivitive.
The current vs Voltage graph for the mixture was very different under illumination.
they predict these sort of flexible polymer photodetectors will be useful in medical imaging.

\cite{Gartner2019a}

Somehow didn't add this!
University of delaware. There is a Jankowski/Marsh image in Fig 1!
OMG I just realised this is Arthi from the MoSDeF calls. :D No wonder this paper is so approachable!! 
Atomistic structures, not always more accurate, can't compute polymer chain level rearrangement
CG -- chemists might not like them but physicists do
atomistic simulations are good when you already know the chain configuration at a state point. Atomistic FF are still tailored to fit the properties of specific systems. got distracted today... will continue with II.B tomorrow
OK back to it
CG - intermediate resolution (group of atoms within a monomer), CG monomer (whole monomer), mesoscale CG model (group of monomers on the length of a Kuhn segment or the whole chain.
Finer models are parameterized to represent specific chemistries while coarse models are more generic. finer models can be parameterized with IBI for structure or force matching or relative entropy matching. the level of coarseness should depend on what features you want to examine.
MARTINI - generic model 3-5 heavy atoms are grouped together each bead is assigned polar/apolar/donor/acceptor etc based on the chemistry/connectivity.
soft potentials can be used for CG beads like DPD -- can have unphysically high compressibility
!!! Systematic coarse graining approaches refs (87,91,269-273)
start reading tomorrow at pt III

@@

\cite{Reith2003a}

IBI algorithm is made in this paper! Uses potentials of mean force. IBI potentials are nontransferrable--they work best for the system they are optimized for.
CG allows chain behavior to be studied. History: bead spring polymer chains in a melt to a soft-core liquid ellipsoidal particles with anisotropic gaussian potential. polymer melt cg-ing. None of these derived an automated optimization scheme to conserve the chemical nature of the underlying atomistic model in a standardized way as we do.
PRISM theory combined with MC can predict long and short range structures of polymer chains but can't produce CG potentials.
Reverce MC can reproduce RDF without a need for potential. lack of potential limits usefulness though because RMC uses knowledge of RDF without knowing underlying forces.
Description of IBI algorithm: potential of mean force IS boltzmann inversion of RDF. (Free energy NOT potential energy.) Bending potentials before nonbonded potentials.
They used a five point running average to smooth the potentials
bond stretch -> angle bend -> nonbonded -> dihedral
They started with monoatomic liquids with LJ and WCA potentials (1) they used the correct potential as V0. (2) then they used the boltzmann inverse of the RDF. 
Conclusions:
start with small range (cutoff?) and increase until RDF matches. CG FF for polyisoprene are different between solution and melt.

\cite{Ayton2007a}

Coarse graining scheme, systematic, for biological systems.
If CGing is done systematicall it retains important averaged atomistic level interations. Connecting length and time scales.Systematic methods for making CG systems: RMC, this paper will focus on multiscale coarse graining (MS-CG) uses force matching algorithm
Variational. Some of the math does not make sense but it appears to only be based on positions of atomistic and CG particles. They make the free energies of the atomisitic and CG systems the same. Many atomistic frames are mapped to CG beads and the potentials are based in the gradient of the forces felt by the beads. The algorithm minimizes a residual function.
Summary: works, RDFs match. Enables calculation of CG force fields without resolving many-dimensional potential of mean force. (but honestly IBI seems so much simpler. Is there something I'm missing? is boltzmann inverse of RDF not PMF?? This paper was published after Reith paper... when is force matching better?)

Review paper- coarse grained models linked to atomistic models. 
They mention the good, marginal, and poor solvent parameter Theta.
models can be linked sequentially, hybrid - both level present at once and interacting, or adaptive - individual molecules switch on the fly depending on e.g., spatial coordinates.
CG target can be thermodynamic or structural.
Structure based: boltzmann inversion of distribution with constant to set minimum to 0. Free energy vs PMF? Boltzmann inversion usually results in a tabulated potential but by fitting to gaussians it can be mapped to an analytical function.
Bonded potential can be determined on a single polymer chain in vacuo but then the nonbonded interactions have to be considered carefully to avoid double counting. However bonded and nonbonded can be obtained from the same atomistic simulation of polymer melt iteratively. This makes the potentials interdepent.
IBI can also consider other thermodynamic quantities like pressure and compressibility. IBI not useful for dilute solutions
start next time at backmapping
backmapping has no one unique soln. every CG structure corresponds to an ensemble of atomistic microstates. reinsert theatomistic structure so that the atoms still satisfy the CG mapping and then relax the atoms with position restraint to the CG position.
CG backmapped to atomistic allows better comparison with experiment than atomistic alone by giving access to larger length and time scales. e.g., NMR timescales are too long to simulate with atomistic alone, yet atomistic coordinates are necessary.
Dynamics: the CG model is independent and has it's own timestep. dynamics are accelerated.

@@

\cite{Brini2013}

review of systematic coarse-graining for soft materials
focuses on representability (how well a system predicts properties at the statepoint it was optimized for) and transferrability ( how well it can be used for other statepoints.)
effective pair potentials are used for CG instead of the expensive many-body potentials. averaging over fast degrees of freddom removes their entropic contribution. to compensate for this, the pair potentials are softer resulting in a smoothed energy landscape. this affects the thermodynamic properties-- e.g., the heat capacity, which is related to the entropy fluctions at constant t and p is underestimated by a cg model (because the fluctuations arent as large). while compressibility related to volume fluctuation will be over estimated (i think because the potentials are so soft.) The thermal expansion coefficient which is related to both may well be represented accurately.
parameterized vs derived CG potentials - 1st one atomistic simulations are used to calculate target properties (pair correlations, force distributions) IBI is this. 2nd one atomistic interaction are used directly. not optimized to reproduce selected tragets, therefore all properties are predictions of the model.
Parameterized methods: IBI method described. 
Inverse Monte Carlo - also an iteractive scheme that corrects a guessed interaction potential in order to reproduce a target radial distribution function, but the guess is based on statistical mechanics that take into account that a variation of the potential at a given distance r can lead to a variation of the RDF at all other distances. more expensive than IBI requires longer sims to calculate correlations. Can also include target thermo properties like surface tension.
Both IBI and IMC are cases of relative entropy -- a measure of the amount of information lost upon coarse-graining and is defined in term of propability distributions of atomistic and CG systems. both methods minimize the discrepancy between the atomistic and CG distributions.
Another method is force matching. effective pair potentials match the mean force on a particle through the atomistic force field.
Derived methods: These potentials have a clear physical meaning (why?) potential of mean force calculated at LOW concentration. fragment based coarse graining
skipped ahead to polymers
polymers are important for cg because the volumes needed to observe their long length scale properties in atomistic md are prohibitively expensive. pressure-corrected IBI scheme for polystyrene matched gyration radius and Flory characteristic ratio at 500 K. (flory ratio relates to chain stiffness?) but entanglement length was overestimated.

\cite{Murtola2009a}

quick letter - to get the full picture we have to consider multiple length scales. abstracting small length scales is necessary for time/resources. probably dont include this in references, it's so short.

\cite{Berendsen2010}

ooh this one looks cool. starts with history of membrane models, goes to cging, then moves to cg dynamics. for next time
many realistic process could not--and would never--be solvable by atomistic simulations. he describes a very simplified model of transport of a single water molecule through a membrane. reduce the system to motion in one reaction coordinate.
the heart of coarse-graining is the reduction of degrees of freedom. then describing the dynamics of the reduced system so that it reproduces the projection of the complete system. this is only possible when the reduced and the removed degrees of freedom are well-separated (the removed are much faster). If the time scales are not separate the dynamic behavior will not be accurate but the probability distributions and thus the thermodynamic properties may still be.
The choice of relevant dof is made on an intuitive basis and depends on what properties are wished to study. Note that atomistic md is already concerned reduced--no electronic dof.
if a CG model does not predict any properties beyond the ones you have used for parameterization--you have achieved nothing! always require your model to predict something unknown.
the motions in reduced space: the equations of motion are no longer hamiltonian--forces depend not only on the present but also the past configuration. Forces proportional to the velocity are non-conservative (kinetic energy is lost). in order to maintain average KE and T noise must be added.
I skimmed the sections on dynamic equations and modelling fluids.
simple methods that are easy to understand and implement--provided they are correct and work--will always prevail over complex methods, even if the latter are more accurate.

\cite{Kim2006}

experiemental paper about effect of p3ht regioregularity in p3ht/fullerene blends on device performance--PCE.
really useful schematic of GIXS experiment. (GIXRD)
interplane pi-pi stacking is parallel to the substrate--enhanced interplane interactions with high RR p3ht benefit vertical (J-V) more than lateral (field-effect) transport. TOF hole mobility in p3ht films show neglible influence of RR. inteplane stacking does not affect vertical transport in pristine crystal. in the blend dark-current densities and TOF mobilities show stronger dependence on regioregularity. highest device efficiency achieved with RR p3ht

\cite{Lee2011}
